The GALEX View of ``Boyajian's Star''

### 2017-08-08 paper/paper.tex
flushing out intro

\documentclass[manuscript, letterpaper]{aastex6}
%\documentclass[twocolumn, trackchanges]{aastex6}
%\documentclass[twocolumn]{aastex6}

\bibliographystyle{aasjournal}

\usepackage{graphicx}
\usepackage[suffix=]{epstopdf}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{url}
\usepackage{xspace}

% from here: https://github.com/dfm/peerless/blob/master/document/ms.tex#L19-L69
% ----------------------------------- %
% start of AASTeX mods by DWH and DFM %
% ----------------------------------- %
\setlength{\voffset}{0in}
\setlength{\hoffset}{0in}
\setlength{\textwidth}{6in}
\setlength{\textheight}{9in}
\setlength{\headheight}{0ex}
\setlength{\headsep}{\baselinestretch\baselineskip} % this is 2 lines in ``manuscript''
\setlength{\footnotesep}{0in}
\setlength{\topmargin}{-\headsep}
\setlength{\oddsidemargin}{0.25in}
\setlength{\evensidemargin}{0.25in}
\linespread{0.54} % close to 10/13 spacing in ``manuscript''
\setlength{\parindent}{0.54\baselineskip}
%\hypersetup{colorlinks = false}
\makeatletter % you know you are living your life wrong when you need to do this
\long\def\frontmatter@title@above{
\vspace*{-\headsep}\vspace*{\headheight}
\noindent\footnotesize
{\noindent\footnotesize\textsc{\@journalinfo}}\par
{\noindent\scriptsize Preprint typeset using \LaTeX\ style AASTeX6\\
With modifications by David W. Hogg and Daniel Foreman-Mackey
}\par\vspace*{-\baselineskip}\vspace*{0.625in}
}%
\makeatother
% Section spacing:
\makeatletter
\let\origsection\section
\renewcommand\section{\@ifstar{\starsection}{\nostarsection}}
\newcommand\nostarsection[1]{\sectionprelude\origsection{#1}}
\newcommand\starsection[1]{\sectionprelude\origsection*{#1}}
\newcommand\sectionprelude{\vspace{1em}}
\let\origsubsection\subsection
\renewcommand\subsection{\@ifstar{\starsubsection}{\nostarsubsection}}
\newcommand\nostarsubsection[1]{\subsectionprelude\origsubsection{#1}}
\newcommand\starsubsection[1]{\subsectionprelude\origsubsection*{#1}}
\newcommand\subsectionprelude{\vspace{1em}}
\makeatother
\widowpenalty=10000
\clubpenalty=10000
\sloppy\sloppypar
% ------------------ %
% end of AASTeX mods %
% ------------------ %

@@

\shorttitle{GALEX View of ``Boyajian's Star''}
\shortauthors{Davenport}

\author{
	James R. A. Davenport\altaffilmark{1,2}
	Riley W. Clarke\altaffilmark{1}
	Zachery Laycock\altaffilmark{1}
	Kevin R. Covey\altaffilmark{1}
	scott flemming\altaffilmark{3}
	tabby boyajian\altaffilmark{4}
	Bernie Shiao\altaffilmark{3}
	chase million\altaffilmark{5}
	Benjamin T. Montet\altaffilmark{6}
	david wilson\altaffilmark{7}
	Manuel Olmedo\altaffilmark{8}
	eric mamajek\altaffilmark{9}
	}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The enigmatic star KIC 8462852, also known as ``Boyajian's Star'',  has puzzled for both its short (days) length dimming events, and a years-long secular dimming observed by the \Kepler mission.
GALEX provides both short timescale sampling from the photon-counting data, and longer baseline data from multiple campaigns that imaged this field/ also providing a wide wavelength baseline to compare with the optical \Kepler data, and provide important constraint for models of this system.
here we investigate both the short and long timescale data. from 4 GALEX visits totaling 1600 seconds of exposure time in 2011, spread over 70 days, we find no coherent NUV variability in the system on 10--100 sec timescales during these time windows. Comparing the integrated flux from these 2011 visits to the 2012 NUV flux published in the GALEX-CAUSE Kepler survey, we find a 3\% decrease in brightness of KIC 8462852. This decrease is the first independent validation of the secular fading reported by \citet{montet2016}. The similar amplitudes between the NUV and optical data rule out typical interstellar dust as the cause of this fading.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

The \Kepler mission \citep{borucki2010}

found this F3 star with strange dips \citet{boyajian2015}. further mystery, the star slowly fades over the time of the \Kepler mission \citet{montet2016}

debated fading also over a century from photographic plate archive \citet{schaefer2016} for, \citet{hippke2016} against.

@@

search for infrared flux excess, no strong detection found
\citep{marengo2015}

@@

%%%%%%%%%%%%%%%%%
\bibliography{/Users/davenpj3/Dropbox/references.bib}

>>>>

%\documentclass[twocolumn, trackchanges]{aastex6}
\documentclass[twocolumn]{aastex6}

%\documentclass[manuscript, letterpaper]{aastex6}

\bibliographystyle{aasjournal}
\usepackage{graphicx}
\usepackage[suffix=]{epstopdf}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{url}
\usepackage{xspace}

%% from here: https://github.com/dfm/peerless/blob/master/document/ms.tex#L19-L69
%% ----------------------------------- %
%% start of AASTeX mods by DWH and DFM %
%% ----------------------------------- %
%\setlength{\voffset}{0in}
%\setlength{\hoffset}{0in}
%\setlength{\textwidth}{6in}
%\setlength{\textheight}{9in}
%\setlength{\headheight}{0ex}
%\setlength{\headsep}{\baselinestretch\baselineskip} % this is 2 lines in ``manuscript''
%\setlength{\footnotesep}{0in}
%\setlength{\topmargin}{-\headsep}
%\setlength{\oddsidemargin}{0.25in}
%\setlength{\evensidemargin}{0.25in}
%\linespread{0.54} % close to 10/13 spacing in ``manuscript''
%\setlength{\parindent}{0.54\baselineskip}
%%\hypersetup{colorlinks = false}
%\makeatletter % you know you are living your life wrong when you need to do this
%\long\def\frontmatter@title@above{
%\vspace*{-\headsep}\vspace*{\headheight}
%\noindent\footnotesize
%{\noindent\footnotesize\textsc{\@journalinfo}}\par
%{\noindent\scriptsize Preprint typeset using \LaTeX\ style AASTeX6\\
%With modifications by David W. Hogg and Daniel Foreman-Mackey
%}\par\vspace*{-\baselineskip}\vspace*{0.625in}
%}%
%\makeatother
%% Section spacing:
%\makeatletter
%\let\origsection\section
%\renewcommand\section{\@ifstar{\starsection}{\nostarsection}}
%\newcommand\nostarsection[1]{\sectionprelude\origsection{#1}}
%\newcommand\starsection[1]{\sectionprelude\origsection*{#1}}
%\newcommand\sectionprelude{\vspace{1em}}
%\let\origsubsection\subsection
%\renewcommand\subsection{\@ifstar{\starsubsection}{\nostarsubsection}}
%\newcommand\nostarsubsection[1]{\subsectionprelude\origsubsection{#1}}
%\newcommand\starsubsection[1]{\subsectionprelude\origsubsection*{#1}}
%\newcommand\subsectionprelude{\vspace{1em}}
%\makeatother
%\widowpenalty=10000
%\clubpenalty=10000
%\sloppy\sloppypar
%% ------------------ %
%% end of AASTeX mods %
%% ------------------ %

@@

\shorttitle{GALEX View of ``Boyajian's Star''}
\shortauthors{Davenport et al.}

\author{
	James R. A. Davenport\altaffilmark{1,2}
	Riley W. Clarke\altaffilmark{1}
	Zachery Laycock\altaffilmark{1}\\
	Kevin R. Covey\altaffilmark{1}
	Scott W. Flemming\altaffilmark{3}
	Tabetha S. Boyajian\altaffilmark{4}
	Benjamin T. Montet\altaffilmark{5}\\
	Bernie Shiao\altaffilmark{3}
	Chase C. Million\altaffilmark{6}
	David J. Wilson\altaffilmark{7}
	Manuel Olmedo\altaffilmark{8}
	Eric E. Mamajek\altaffilmark{9}
	}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The enigmatic star KIC 8462852, also known as ``Boyajian's Star'',  has puzzled for both its short (days) length dimming events, and a years-long secular dimming observed by the \Kepler mission.
GALEX provides both short timescale sampling from the photon-counting data, and longer baseline data from multiple campaigns that imaged this field/ also providing a wide wavelength baseline to compare with the optical \Kepler data, and provide important constraint for models of this system.
here we investigate both the short and long timescale data. from 4 GALEX visits totaling 1600 seconds of exposure time in 2011, spread over 70 days, we find no coherent NUV variability in the system on 10--100 sec timescales during these time windows. Comparing the integrated flux from these 2011 visits to the 2012 NUV flux published in the GALEX-CAUSE Kepler survey, we find a 3\% decrease in brightness of KIC 8462852. This decrease is the first  validation of the secular fading reported by \citet{montet2016} not in optical wavelengths. The similar amplitudes between the NUV and optical data rule out typical interstellar dust as the cause of this fading.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
KIC 8462852, also known as ``Boyajian's Star'', is an unusual F3 dwarf in the \Kepler field that has exhibited unexplained optical variability on a variety of timescales. The initial discovery was of several dramatic, short timescale (days) dimming events with amplitudes up to 20\% in the \Kepler 30-min cadence data \citep{boyajian2015}. Though the \Kepler mission \citep{borucki2010} obtained data at a 30-min cadence for $\sim$4 years on this star, no definitive pattern or cycle was found, nor has any single explanation for this variability been accepted by the community \citep{wright2016b}.

Analysis of archival optical photographic plates has found that KIC 8462852 may have additionally faded nearly 16\% over the past century \citep{schaefer2016}. Such a precise measurement for a single star is difficult, and the result has been debated \citep{hippke2016}. However, using the 53 ``Full Frame Images'' (FFIs) spread over the 4-year \Kepler mission, \citet{montet2016} were able to trace the brightness of KIC 8462852 using an independent flux calibration. The resulting flux-calibrated FFI light curve showed definitively that KIC 8462852 faded by more than 3\% over 4 years. %This long timescale variability has recently been confirmed with an analysis of archival ground-based photometry (Simon et al. 2017 in prpe)

The short (days) and long (years) timescale variability discovered for KIC 8462852 has presented a unique set of observational constraints on any single model used to describe the system. For example, if variable dust extinction is responsible for both temporal features, then it must have a wildly variable density distribution on small spatial scales, and a small density gradient over large spatial scales. Searches for an infrared flux excess consistent with a foreground or circumstellar dust shell have to date found no strong detection \citep{marengo2015}.

Since optical variability alone has not produced a single explanation for KIC 8462852, multi-wavelength studies are needed to constrain nature of the long timescale fading and short timescale dimming. Follow-up multi-band photometric and spectroscopic campaigns are underway\footnote{\url{http://www.wherestheflux.com}}, which will provide an improved understanding of any future ``dips''.

@@

@@

%%%%%%%%%%%%%%%%%
\bibliography{/Users/james/Dropbox/references.bib}
